---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## Example

```{r example}
library(testbindrows)
library(dplyr, warn.conflicts = FALSE)
```

```{r}
x <- df_special(x = 1, y = 2)
y <- data.frame(x = 1, y = 2)

bind_rows(x, y)

# it is the right class
class(bind_rows(x, y))

# reverse order calls normal data frame method
class(bind_rows(y, x))
```

```{r}
x <- df_next_method(x = 1, y = 2)
y <- data.frame(x = 1, y = 2)

bind_rows(x, y)

# it is the right class
class(bind_rows(x, y))

# reverse order calls normal data frame method
class(bind_rows(y, x))
```


This class doesn't have the `.id` argument used in the data frame method of `bind_rows()`. That's totally fine with R CMD check since the generic for `bind_rows()` is just `...`.

Since `bind_rows_dots()` removes the unmatched `.id` argument from the equation, users can technically call `bind_rows()` with `.id` and it will just get silently ignored.

This generally bodes well for us, as it means we can add extra optional arguments to the data frame method of `bind_rows()` in the future, and it won't immediately break anything. In the worst case it will just result in silent no-op behavior.

```{r}
x <- df_no_id(x = 1, y = 2)
y <- data.frame(x = 1, y = 2)

bind_rows(x, y)

# ignored
bind_rows(x, y, .id = "foo")

# used because we go through the data frame method
bind_rows(y, x, .id = "foo")
```

This class has an _extra_ argument, `.copy`, that isn't present in the generic or the data.frame method. That's also fine. Again, `bind_rows_dots()` ignores it for the purpose of dispatch, and if we hit the data frame method then `bind_rows_dots()` there will ignore it again because the data frame method doesn't know about that argument.

```{r}
x <- df_extra(x = 1, y = 2)
y <- data.frame(x = 1, y = 2)

bind_rows(x, y)

# used in the df_extra method
bind_rows(x, y, .copy = TRUE)

# ignored
bind_rows(y, x, .copy = TRUE)
```
